Gammapy: A Python package for gamma-ray astronomy

### 2023-06-01 src/ms-review.tex
Fix empty reference and observation length range

%% Context
%% CN: I think Fermi-LAT data were available from the 2nd year on
%% https://fermi.gsfc.nasa.gov/ssc/data/policy/
While \fermi data and analysis tools have been public from the
beginning \citep{}, ground-based \gammaray astronomy has been historically conducted
through experiments operated by independent collaborations, each relying
on their own proprietary data and analysis software developed as part of the
instrument. While this model has been so far successful, it does not
permit easy combination of data from several instruments. This lack of
interoperability currently limits the full exploitation of the
available \gammaray data, especially in light of the fact that different instruments often have
complementary sky coverages, and the various detection
techniques have complementary properties in terms of energy range covered,
duty cycle and spatial resolution.

@@

\subsection{gammapy.data}
\label{ssec:gammapy-data}
The \code{gammapy.data} sub-package implements the functionality to select,
read, and represent DL3 \gammaray data in memory. It provides the main user
interface to access the lowest data level. \gammapy currently only
supports data that is compliant with \code{v0.2} and \code{v0.3} of the \gadf data format.
DL3 data are typically bundled into individual observations, corresponding to
stable periods of data acquisition. For IACT instruments, for which the \gadf
data model and \gammapy were initially conceived, this duration is typically 
$20 - 30\,{\rm min}$. Each observation is assigned a unique integer ID for reference.

>>>>

%% Context
%% CN: I think Fermi-LAT data were available from the 2nd year on
%% https://fermi.gsfc.nasa.gov/ssc/data/policy/
While \fermi data and analysis tools have been public from the
beginning \citep{Atwood2009}, ground-based \gammaray astronomy has been historically conducted
through experiments operated by independent collaborations, each relying
on their own proprietary data and analysis software developed as part of the
instrument. While this model has been so far successful, it does not
permit easy combination of data from several instruments. This lack of
interoperability currently limits the full exploitation of the
available \gammaray data, especially in light of the fact that different instruments often have
complementary sky coverages, and the various detection
techniques have complementary properties in terms of energy range covered,
duty cycle and spatial resolution.

@@

\subsection{gammapy.data}
\label{ssec:gammapy-data}
The \code{gammapy.data} sub-package implements the functionality to select,
read, and represent DL3 \gammaray data in memory. It provides the main user
interface to access the lowest data level. \gammapy currently only
supports data that is compliant with \code{v0.2} and \code{v0.3} of the \gadf data format.
DL3 data are typically bundled into individual observations, corresponding to
stable periods of data acquisition. For IACT instruments, for which the \gadf
data model and \gammapy were initially conceived, this duration is typically 
$15 - 30\,{\rm min}$. Each observation is assigned a unique integer ID for reference.
